% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{url}
\usepackage{xcolor}
\definecolor{accent}{HTML}{1F3A5F}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}
% accent-coloured section headers + rule (baseline only)
\titleformat{\section}
  {\Large\scshape\raggedright\color{accent}}
  {}{0em}
  {}
  [{\color{accent}\titlerule}]

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{\textcolor{accent}{Jonathan Xu}}
\vspace{-0.3ex}
\centerline{\large\itshape\textcolor{accent}{Senior Software Engineer \textperiodcentered\ Platform \& Cloud Engineering}}
\vspace{0.9ex}

\basicInfo{
  \email{jonathanilc@hotmail.com} \textperiodcentered\ 
  \phone{(+64) 21-026-24525} \textperiodcentered\ 
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}
  \textperiodcentered\ \github[Jonathanilc]{https://github.com/Jonathanilc}}
  \vspace{2em}

\section*{Summary}
Senior Software Engineer with 10+ years across backend development, cloud infrastructure, and platform engineering. On IDEXX's platform team I build the internal developer platform that takes services from Git to AWS—Go tooling, Kubernetes/Helm, Terraform, GitHub Actions, ArgoCD GitOps, and Datadog observability—and led the Go billing platform serving 5k+ sites and 9k hospitals with SAP integration. Strong full-stack range (React, Angular), with a track record of cross-functional delivery and mentoring. Auckland-based NZ citizen, eligible to work in Australia (Subclass 444).

\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2025 -- Present} \\
Platform engineering: building VetSoft Deploy (VSD), the internal developer platform that takes a service from Git repo to running on AWS, alongside modernizing the Go billing platform.
\begin{itemize}
  \item Build and maintain VetSoft Deploy (VSD), an internal developer platform that standardizes how services ship to AWS—spanning a Go CLI, a webhook API, Helm charts, a Terraform module, and reusable GitHub Actions workflows.
  \item Developed vetsoft-cli, a Go command-line tool (distributed as a Homebrew cask) that scaffolds and updates services, giving teams a self-service golden path to production.
  \item Automated per-service AWS provisioning with Terraform—OIDC IAM roles and ECR repositories across all environments—managed from a source-of-truth monorepo.
  \item Deploy services to Kubernetes (EKS) using Helm and ArgoCD GitOps, with Datadog for observability and operational visibility.
  \item Led the Go billing platform refactor to a vertical-slice architecture with an OpenAPI-driven API layer, delivered incrementally with no disruption to the live pipeline.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2024 -- 2025} \\
Delivered the billing project: collect and calculate billing data from 5k+ sites and 9k hospitals, then sync to SAP to generate monthly invoices for clients.
\begin{itemize}
  \item Designed and built the self-service client application (React, Tailwind, Vite) used by the billing team for billing operations and configuration.
  \item Developed Golang backend services for billing data aggregation, validation, and pipeline orchestration.
  \item Owned the SAP integration layer; ensured reliable data delivery for monthly invoice generation.
  \item Enabled the billing team by shipping new features and maintaining the platform used across multiple internal users.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar, a full-stack JavaScript application: client hosted on S3, services on ECS (Fargate).
\begin{itemize}
  \item Owned the client-side application (React, Context API), shipping core product features.
  \item Developed and maintained the server-side application (Node.js, Express) powering the product.
  \item Managed AWS infrastructure as code with Terraform across multiple services; improved deployment reliability and operational visibility.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom e-commerce solutions for clients on Shopify and BigCommerce.
\begin{itemize}
  \item Integrated Shopify with third-party stock management systems to streamline inventory and order flows.
  \item Built custom micro-frontend apps embedded in Shopify storefronts, enabling client-specific functionality.
  \item Coached and mentored junior team members; supported their growth and code quality.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom e-commerce sites on Shopify and BigCommerce; drove DevOps and automation.
\begin{itemize}
  \item Automated the release process and CI/CD pipelines, reducing deploy time and enabling more frequent, reliable releases.
  \item Developed reusable website components used across multiple client projects.
\end{itemize}


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Cloud \& Platform:} AWS (ECS/Fargate, S3, ECR, VPC, OIDC/IAM), Kubernetes (EKS), Helm, internal developer platforms
  \item \textbf{DevOps \& CI/CD:} Terraform, ArgoCD (GitOps), GitHub Actions, GitLab CI, Docker, Datadog, Git
  \item \textbf{Backend:} Golang, Node.js, Python, Flask, C\#, .NET Core, REST/OpenAPI, GraphQL
  \item \textbf{Architecture:} Microservices, clean \& vertical-slice architecture, OpenAPI contracts, cloud-native
  \item \textbf{Frontend:} React, Angular, TypeScript, JavaScript, HTML, CSS, Tailwind
  \item \textbf{Best Practices:} SOLID, design patterns, clean code, TDD/unit testing, Agile, mentoring \& code review
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect – Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Work eligibility: NZ citizen, eligible to work in Australia (Subclass 444 SCV)
  \item Languages: English – Fluent, Mandarin – Native speaker
\end{itemize}
\end{document}
