% !TEX program = xelatex
% Variant: IoT backend / distributed systems (Senior Back-End Engineer).
% Source: Sourced (NZ) — IoT connected platform for construction equipment / asset fleets.
% Angle: lead with Node.js + large-scale distributed data on AWS. NZ working rights surfaced.

\documentclass{resume}
\usepackage{url}

\begin{document}
\pagenumbering{gobble}

\name{Jonathan Xu}

\basicInfo{
  \email{jono\_x@icloud.com} \textperiodcentered\
  \phone{(+64) 21-026-24525} \textperiodcentered\
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}}
  \vspace{2em}

\section*{Summary}
Senior Backend Engineer with 10+ years building and operating production distributed systems, with strong JavaScript/Node.js alongside Go and Python on AWS. At IDEXX, designed a large-scale data pipeline that aggregates and reconciles data from 5k+ sites and 9k hospitals before syncing to SAP. Comfortable across microservices, container deployments, and high-volume data. Based in Auckland with full New Zealand working rights. AWS Certified Solutions Architect -- Professional.

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}


\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer -- VetSoft Platform Team} \hfill \textit{2025 -- Present} \\
Leading a billing-platform refactor to a vertical-slice architecture with an OpenAPI-driven REST API layer.
\begin{itemize}
  \item Migrated the codebase to vertical slice architecture for domain alignment and maintainability.
  \item Introduced OpenAPI as the source of truth for the API layer, enabling generated clients and contract testing.
  \item Delivered the migration incrementally while keeping the production pipeline operational.
  \item Build and maintain VetSoft Deploy (VSD), an internal developer platform that standardizes how services ship to AWS: a Go CLI, Helm charts, a Terraform module, and reusable GitHub Actions workflows.
  \item Deploy services to Kubernetes (EKS) with Helm and ArgoCD GitOps and Datadog observability; provision per-service OIDC IAM roles and ECR repositories with Terraform.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer -- VetSoft Platform Team} \hfill \textit{2024 -- 2025} \\
Designed and built a high-volume billing data pipeline aggregating and reconciling data from 5k+ sites and 9k hospitals, then syncing to SAP for monthly invoicing.
\begin{itemize}
  \item Built backend services for data aggregation, validation, and pipeline orchestration at scale.
  \item Owned the SAP integration layer; ensured reliable, idempotent delivery with reconciliation against source data.
  \item Modelled relational data (SQL) for billing aggregation; shipped the internal self-service app used by the billing team.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer -- Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar across the full JavaScript stack -- Node.js/Express services on ECS (Fargate), client on S3.
\begin{itemize}
  \item Developed and maintained Node.js/Express microservices powering the product.
  \item Managed AWS infrastructure as code with Terraform (ECS/Fargate, S3, VPC, networking); improved deployment reliability and operational visibility.
  \item Containerised services with Docker and shipped core product features end-to-end.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom e-commerce solutions for clients on Shopify and BigCommerce.
\begin{itemize}
  \item Integrated Shopify with third-party stock-management and ERP systems to streamline inventory and order flows.
  \item Built backend integrations and micro-frontend apps embedded in Shopify storefronts.
  \item Coached and mentored junior team members through code reviews and technical guidance.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom e-commerce sites; drove DevOps and automation.
\begin{itemize}
  \item Automated the release process and CI/CD pipelines, reducing deploy time and enabling more frequent, reliable releases.
  \item Built reusable backend integrations and components across client projects.
  \item Wrote and maintained unit tests to protect critical paths and enable confident refactoring.
\end{itemize}


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Backend: Node.js, JavaScript, TypeScript, Golang, Python, C\#, .NET Core, RESTful APIs, GraphQL
  \item Data: SQL / relational modelling, large-scale data pipelines, aggregation \& reconciliation, SAP integration
  \item Cloud \& Infra (AWS): EC2, ECS/Fargate, S3, VPC, ECR, Kubernetes (EKS), Helm, Terraform, Docker
  \item Architecture \& Design: microservices, vertical-slice / clean architecture, OpenAPI-driven contracts
  \item DevOps \& CI/CD: GitHub Actions, GitLab CI, ArgoCD (GitOps), Datadog, automated release pipelines
  \item Best Practices: SOLID, design patterns, TDD/unit testing, Agile delivery, mentoring \& code review
  \item Frontend (full-stack contexts): React, HTML, CSS, Tailwind
\end{itemize}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect -- Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: \url{https://github.com/Jonathanilc}
  \item Full New Zealand working rights; available for contract / remote work
  \item Languages: English -- Fluent, Mandarin -- Native speaker
\end{itemize}
\end{document}
