% !TEX program = xelatex
% Variant: Potentia — Senior Integration Developer cover letter.
% Source: https://nz.seek.com/job/92081881

\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}

\definecolor{accent}{HTML}{0066CC}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}
\pagenumbering{gobble}

\begin{document}

\begin{flushright}
{\Large\textbf{Jonathan Xu}}\\[0.3em]
\faEnvelope\ \href{mailto:jonathanilc@hotmail.com}{jonathanilc@hotmail.com} \\
\faPhone\ (+64) 21-026-24525 \\
\faLinkedin\ \href{https://www.linkedin.com/in/jonathan-x-4aba55115}{jonoxu}
\end{flushright}

\vspace{0.5em}

\today

\vspace{0.5em}

Hiring Team \\
Potentia \\
Wellington, New Zealand

\vspace{0.5em}

Dear Hiring Team,

I am writing to apply for the Senior Integration Developer contract role advertised on Seek (ref 92081881). The brief — integrations for an enterprise LMS, REST APIs and middleware, Python and PostgreSQL, working autonomously across a distributed team — describes the kind of work I have been doing in production for the past several years, and I would be excited to bring that experience to your project.

At IDEXX, I own the integration between our billing platform and SAP: a pipeline that aggregates and reconciles data from 5,000+ veterinary sites and 9,000 hospitals every month before invoicing through SAP. The work has spanned schema mapping, idempotent delivery and retries, reconciliation against source-of-truth data, and close collaboration with both internal stakeholders and the vendor side — exactly the kind of enterprise integration challenge your role describes. More recently I have been driving an OpenAPI-first REST API layer on top of that platform so the contracts are explicit, versioned, and consumable by other teams without ambiguity.

Earlier in my career at Moustache Republic I built integrations between Shopify storefronts and third-party stock-management and ERP systems — a useful counterpoint to the IDEXX work, because it taught me how to move quickly across unfamiliar vendor APIs, write small middleware layers, and ship reliable integrations under tight client timelines. That pragmatic, "pick up the stack and deliver" approach is something I would bring directly to your LMS project.

Python is in my regular toolkit (Flask) alongside Go and Node.js, and I am comfortable in PostgreSQL and relational data modelling. I work well in distributed teams — most of my recent roles have been remote across regions — and I am based in Auckland with full New Zealand working rights, available to start as soon as needed for the contract.

I would welcome the opportunity to discuss how my integration background could contribute to Potentia's LMS implementation. Thank you for your consideration.

\vspace{0.5em}

Sincerely, \\
Jonathan Xu

\end{document}
