% !TEX program = xelatex
% Variant: Potentia — Senior Integration Developer (6-month contract, Wellington / remote NZ)
% JD: Python + PostgreSQL, REST APIs, integration/middleware for an enterprise LMS.
% Source: https://nz.seek.com/job/92081881

\documentclass{resume}
\usepackage{url}

\begin{document}
\pagenumbering{gobble}

\name{Jonathan Xu}

\basicInfo{
  \email{jonathanilc@hotmail.com} \textperiodcentered\
  \phone{(+64) 21-026-24525} \textperiodcentered\
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}}
  \vspace{2em}

\section*{Summary}
Senior backend engineer with 10+ years of experience designing and operating integration and middleware systems between large enterprise platforms. At IDEXX, owns the SAP integration and billing pipeline that aggregates and reconciles data from 5k+ sites and 9k hospitals every month. Comfortable in Python, Go, and Node.js; works autonomously in distributed teams. NZ citizen / full working rights.

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}


\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2025 -- Present} \\
Leading a backend refactor with an OpenAPI-driven REST API layer — standardising contracts across internal and external consumers.
\begin{itemize}
  \item Introduced OpenAPI as the source of truth for the API layer, enabling generated clients, contract testing, and consistent documentation across teams.
  \item Migrated the codebase to a vertical-slice architecture aligned to integration boundaries, improving maintainability and reducing coupling between subsystems.
  \item Delivered the migration incrementally while keeping the production billing pipeline operational.
  \item Build and maintain VetSoft Deploy (VSD), an internal developer platform that standardizes how services ship to AWS: a Go CLI, Helm charts, a Terraform module, and reusable GitHub Actions workflows.
  \item Deploy services to Kubernetes (EKS) with Helm and ArgoCD GitOps and Datadog observability; provision per-service OIDC IAM roles and ECR repositories with Terraform.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2024 -- 2025} \\
Designed and built the enterprise integration that connects the ezyVet billing pipeline to SAP for monthly invoicing — operating across 5k+ veterinary sites and 9k hospitals.
\begin{itemize}
  \item Owned the SAP integration layer end-to-end: schema mapping, idempotent delivery, retries, and reconciliation against source-of-truth data.
  \item Built backend services for data aggregation, validation, and pipeline orchestration with strong observability and audit trails.
  \item Worked across the wider project team and external vendors to align on contracts, edge cases, and cutover plans.
  \item Shipped a self-service internal application (React/Vite) used by the billing team to configure and operate the pipeline.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar — Node.js services on ECS (Fargate) with a React client on S3.
\begin{itemize}
  \item Developed and maintained Node.js / Express services exposing RESTful APIs consumed by the client and partner systems.
  \item Managed AWS infrastructure as code with Terraform across multiple services; improved deployment reliability and operational visibility.
  \item Worked in a fully distributed team across regions, collaborating asynchronously on design and delivery.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom e-commerce integrations for clients on Shopify and BigCommerce — primarily connecting storefronts to third-party stock management and ERP systems.
\begin{itemize}
  \item Integrated Shopify with third-party stock management systems via REST APIs and webhooks, automating inventory and order flows.
  \item Built middleware components and micro-frontend apps embedded in Shopify storefronts to expose client-specific functionality.
  \item Conducted early-phase research and feasibility studies for new integrations across diverse vendor APIs.
  \item Coached and mentored junior team members; wrote and maintained technical documentation.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom e-commerce sites and drove automation.
\begin{itemize}
  \item Built API integrations and reusable middleware between Shopify storefronts and client back-office systems.
  \item Automated the release process and CI/CD pipelines, reducing deploy time and enabling more frequent, reliable releases.
  \item Wrote and maintained unit tests to protect critical integration paths.
\end{itemize}


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Integration \& Middleware: REST APIs, OpenAPI / contract-first design, webhooks, message-driven pipelines, SAP integration, ERP / third-party vendor APIs
  \item Languages: Python (Flask), Golang, Node.js, TypeScript, C\#/.NET Core
  \item Databases: PostgreSQL, relational data modelling, schema migrations
  \item Cloud \& Infra (AWS): ECS/Fargate, S3, ECR, Kubernetes (EKS), Helm, Terraform, Docker; GitHub Actions, ArgoCD (GitOps), Datadog
  \item Architecture: microservices, vertical-slice / clean architecture, idempotent pipelines, observability
  \item Ways of working: distributed / remote teams, autonomous delivery, stakeholder \& vendor communication, Agile
\end{itemize}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect – Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: \url{https://github.com/Jonathanilc}
  \item Languages: English – Fluent, Mandarin – Native speaker
  \item Working rights: full New Zealand working rights
\end{itemize}
\end{document}
