% !TEX program = xelatex
% Variant: Backend-focused
% Tailored for backend / platform / distributed systems roles.
% Skills are reordered to lead with Go, cloud, and architecture.

\documentclass{resume}
\usepackage{url}

\begin{document}
\pagenumbering{gobble}

\name{Jonathan Xu}

\basicInfo{
  \email{jonathanilc@hotmail.com} \textperiodcentered\
  \phone{(+64) 21-026-24525} \textperiodcentered\
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}}
  \vspace{2em}

\section*{Summary}
Senior Backend Engineer with 10+ years of experience designing and operating production systems in Go, Node.js, and Python on AWS. At IDEXX, owns the billing pipeline for 5k+ sites and 9k hospitals, including SAP integration and a Go-based aggregation pipeline. AWS Certified Solutions Architect – Professional.

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}


\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2025 -- Present} \\
Leading a Go billing system refactor: horizontal to vertical-slice architecture, with an OpenAPI-driven API layer.
\begin{itemize}
  \item Migrated the Go codebase to vertical slice architecture for domain alignment and maintainability.
  \item Introduced OpenAPI as the source of truth for the API layer, enabling generated clients and contract testing.
  \item Delivered the migration incrementally while keeping the production billing pipeline operational.
  \item Build and maintain VetSoft Deploy (VSD), an internal developer platform that standardizes how services ship to AWS: a Go CLI, Helm charts, a Terraform module, and reusable GitHub Actions workflows.
  \item Deploy services to Kubernetes (EKS) with Helm and ArgoCD GitOps and Datadog observability; provision per-service OIDC IAM roles and ECR repositories with Terraform.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2024 -- 2025} \\
Designed and built the billing pipeline that aggregates and reconciles data from 5k+ sites and 9k hospitals and syncs it to SAP for monthly invoicing.
\begin{itemize}
  \item Built Go backend services for data aggregation, validation, and pipeline orchestration.
  \item Owned the SAP integration layer; ensured reliable, idempotent delivery for monthly invoice generation.
  \item Shipped the internal self-service application (React/Vite) used by the billing team for ops and configuration.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar — services on ECS (Fargate), client on S3 — across the full JavaScript stack.
\begin{itemize}
  \item Developed and maintained Node.js/Express services powering the product.
  \item Managed AWS infrastructure as code with Terraform across multiple services; improved deployment reliability and operational visibility.
  \item Owned the React client and shipped core product features end-to-end.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom e‑commerce solutions for clients on Shopify and BigCommerce.
\begin{itemize}
  \item Integrated Shopify with third-party stock management systems to streamline inventory and order flows.
  \item Built backend integrations and micro-frontend apps embedded in Shopify storefronts.
  \item Coached and mentored junior team members.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom e‑commerce sites; drove DevOps and automation.
\begin{itemize}
  \item Automated the release process and CI/CD pipelines, reducing deploy time and enabling more frequent, reliable releases.
  \item Built reusable backend integrations and components across client projects.
  \item Wrote and maintained unit tests to protect critical paths and enable confident refactoring.
\end{itemize}


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Backend: Golang, Node.js, Python, Flask, C\#, .NET Core, RESTful APIs, GraphQL
  \item Cloud \& Infra (AWS): ECS/Fargate, S3, ECR, OIDC/IAM, Kubernetes (EKS), Helm, Terraform, Docker
  \item Architecture \& Design: microservices, vertical-slice / clean architecture, OpenAPI-driven contracts, internal developer platforms, SAP integration
  \item DevOps \& CI/CD: GitHub Actions, GitLab CI, ArgoCD (GitOps), Datadog, automated release pipelines
  \item Best Practices: SOLID, design patterns, TDD/unit testing, Agile delivery
  \item Frontend (working knowledge): React, TypeScript, Tailwind
\end{itemize}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect – Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: \url{https://github.com/Jonathanilc}
  \item Languages: English – Fluent, Mandarin – Native speaker
\end{itemize}
\end{document}
