% !TEX program = xelatex
% Variant: Dave Clark Design -- Full-Stack Engineer (4-month initial contract).
% Source: pasted JD (no URL); via recruiter Alex. Company: https://www.daveclarkdesign.com/en-nz/
% Angle: lead with React + Node.js/TypeScript + AWS + REST on SaaS product builds;
%        surface enterprise-scale SaaS (billing platform, Vet Radar) for big-business clients
%        (banks, finservices, large tech). Auckland-based, contract availability surfaced.
% Design: merged with latest baseline (deep-navy accent, role tagline, GitHub in header,
%        accent section headers, colored links, bold skill labels).
% Honest: serverless specifics (Lambda, API Gateway, DynamoDB, Serverless Framework) are
%        Solutions Architect -- Professional breadth, not hands-on (hands-on AWS is ECS/Fargate,
%        S3, VPC, ECR, IAM/OIDC). mTLS / ECDH-ECDSA crypto intentionally not raised (candidate
%        preference); resume keeps a truthful Security line (IAM/OIDC, TLS, secure SAP integration).

\documentclass{resume}
\usepackage{url}
\usepackage{xcolor}
\definecolor{accent}{HTML}{1F3A5F}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}
% accent-coloured section headers + rule (merged from baseline)
\titleformat{\section}
  {\Large\scshape\raggedright\color{accent}}
  {}{0em}
  {}
  [{\color{accent}\titlerule}]

\begin{document}
\pagenumbering{gobble}

\name{\textcolor{accent}{Jonathan Xu}}
\vspace{-0.3ex}
\centerline{\large\itshape\textcolor{accent}{Senior Software Engineer \textperiodcentered\ Full-Stack \& SaaS Product}}
\vspace{0.9ex}

\basicInfo{
  \email{jono\_x@icloud.com} \textperiodcentered\
  \phone{(+64) 21-026-24525} \textperiodcentered\
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}
  \textperiodcentered\ \github[Jonathanilc]{https://github.com/Jonathanilc}}
  \vspace{2em}

\section*{Summary}
Senior Full-Stack Engineer with 10+ years building and operating SaaS products on AWS, with React and Node.js/TypeScript at the centre alongside Go and Python. At IDEXX I design, ship, and run product platforms the business depends on -- a billing platform serving 5k+ sites and 9k hospitals with SAP integration, and the Vet Radar product across a React client and Node.js services on AWS -- behind REST / OpenAPI-driven APIs. I enjoy moving across the full stack and bringing ideas to product builds for demanding clients. Auckland-based with full New Zealand working rights, available for the 4-month initial contract. AWS Certified Solutions Architect -- Professional.

\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer -- VetSoft Platform Team} \hfill \textit{2025 -- Present} \\
Building VetSoft Deploy (VSD) -- the internal platform that automates shipping product services to AWS -- and leading the billing platform's refactor to a vertical-slice architecture behind an OpenAPI-driven REST API.
\begin{itemize}
  \item Build and maintain VetSoft Deploy (VSD), an internal developer platform that takes a service from Git to running on AWS, giving product teams a self-service path to production.
  \item Automate AWS provisioning as code with Terraform (per-service IAM/OIDC roles and ECR repositories) and reusable GitHub Actions CI/CD workflows, removing manual setup and standardising how teams ship.
  \item Built the supporting webhook API and a CLI (distributed as a Homebrew cask) that scaffold, configure, and deploy services for engineers across the organisation.
  \item Introduced OpenAPI as the single source of truth for the billing REST API -- generated clients, contract testing, and docs that stay in sync -- with GitOps-based deploys and Datadog observability throughout.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer -- VetSoft Platform Team} \hfill \textit{2024 -- 2025} \\
Designed, built, and operate a high-volume billing platform aggregating and reconciling data from 5k+ sites and 9k hospitals, then syncing to SAP for monthly invoicing.
\begin{itemize}
  \item Designed and shipped the self-service client application (React, Tailwind, Vite) used by the billing team for operations and configuration.
  \item Built backend services for data aggregation, validation, and pipeline orchestration; kept them reliable under real billing load.
  \item Owned the secure SAP integration layer, ensuring reliable, idempotent data delivery for the monthly invoice run.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer -- Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar, a full-stack SaaS product -- React (TypeScript) client hosted on S3, Node.js/Express services on AWS ECS (Fargate).
\begin{itemize}
  \item Owned the client-side application (React, TypeScript, Context API), shipping core product features end to end.
  \item Built and maintained the Node.js/Express services and REST APIs powering the product, containerised with Docker on ECS/Fargate.
  \item Managed the AWS footprint (S3, VPC, networking) as code with Terraform; improved deployment reliability and operational visibility.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom commerce solutions and product integrations for clients on Shopify and BigCommerce.
\begin{itemize}
  \item Built React-based micro-frontend apps embedded in client storefronts, enabling client-specific functionality.
  \item Integrated storefronts with third-party stock-management and ERP systems over REST APIs to streamline inventory and order flows.
  \item Coached and mentored junior engineers through code review and technical guidance.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom commerce sites; drove DevOps and automation.
\begin{itemize}
  \item Automated the release process and CI/CD pipelines, reducing deploy time and enabling more frequent, reliable releases.
  \item Built reusable frontend components and backend integrations across client projects.
\end{itemize}


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Frontend:} React, TypeScript, JavaScript, HTML, CSS, Tailwind
  \item \textbf{Backend:} Node.js, RESTful APIs / OpenAPI, Golang, Python, C\#/.NET Core, GraphQL
  \item \textbf{Cloud (AWS):} hands-on with S3, ECS/Fargate, VPC, ECR, IAM/OIDC; serverless \& event-driven breadth (Lambda, API Gateway, DynamoDB, SNS/SQS, CloudFront, Serverless Framework) as AWS Solutions Architect -- Professional
  \item \textbf{Architecture:} SaaS product platforms, microservices, event-driven \& serverless patterns, REST/OpenAPI contracts, clean / vertical-slice architecture
  \item \textbf{DevOps \& CI/CD:} Terraform, GitHub Actions, Docker, Kubernetes (EKS) / Helm, ArgoCD, Datadog, Git
  \item \textbf{Security:} IAM/OIDC, TLS, secure third-party API integrations (SAP)
  \item \textbf{Practices:} SOLID, TDD/unit testing, Agile delivery, code review \& mentoring; comfortable with AI-assisted development tools
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect -- Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Auckland-based with full New Zealand working rights; available for the 4-month initial contract
  \item Languages: English -- Fluent, Mandarin -- Native speaker
\end{itemize}
\end{document}
