% !TEX program = xelatex
% Variant: Everbridge -- Staff Software Engineer cover letter.
% Sibling of variants/everbridge-staff/resume.tex -- pair as one application.
% Source: https://www.linkedin.com/jobs/view/4423320851/
% Angle: Staff-level full-stack React+Node+AWS, architecture/scale, AI-assisted,
%        technology-agnostic; honest on Java; ties to Everbridge's "keep people safe" mission.

\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}

\definecolor{accent}{HTML}{0066CC}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}
\pagenumbering{gobble}

\begin{document}

\begin{flushright}
{\Large\textbf{Jonathan Xu}}\\[0.3em]
\faEnvelope\ \href{mailto:jono_x@icloud.com}{jono\_x@icloud.com} \\
\faPhone\ (+64) 21-026-24525 \\
\faLinkedin\ \href{https://www.linkedin.com/in/jonathan-x-4aba55115}{jonoxu}
\end{flushright}

\vspace{0.5em}

\today

\vspace{0.5em}

Hiring Team \\
Everbridge \\
Auckland, New Zealand

\vspace{0.5em}

Dear Hiring Team,

I am writing to apply for the Staff Software Engineer role at Everbridge. Building and operating large-scale, full-stack applications and APIs on AWS -- React and Node.js front to back -- is exactly the work I have spent the past decade doing, and the mission behind it draws me in: software that helps keep people safe has to be reliable, and reliability under real load is what I care most about as an engineer. I am based in Auckland with full New Zealand working rights.

My most direct match is the Vet Radar team at IDEXX, where I delivered the product across the full stack: a React client backed by Node.js/Express APIs, containerised with Docker and running on AWS (ECS/Fargate, S3), with the surrounding infrastructure managed as code in Terraform. I owned features end to end -- from the UI through the services to the infrastructure -- and kept the web application and APIs stable in production, which is the kind of complete-lifecycle ownership the role describes.

At the staff level, the part of the job I am most eager to do is shape architecture and lift the whole team. I currently lead the re-architecture of IDEXX's enterprise billing platform -- a system aggregating and reconciling data from 5,000+ sites and 9,000 hospitals each month -- moving it to a vertical-slice design with an OpenAPI-driven REST API so contracts, clients, and documentation stay in sync across teams. Alongside the design work I lead code reviews, mentor engineers, and deliver large changes incrementally without disrupting a pipeline the business depends on every billing cycle.

I will be straight about one thing in your stack: my statically-typed and enterprise work has been in C\#/.NET and Go rather than Java. But moving between languages is how I already work -- Go, Node, Python, and C\# all sit in my day-to-day -- so ramping on Java is a short step, and it fits the technology-agnostic, adaptable approach the role values. I also use agentic AI coding tools every day and have built AI into my development workflow, so the eagerness you are looking for around AI solutions is already how I operate rather than something I would be starting from scratch.

I would welcome the chance to discuss how my full-stack, architecture, and AWS experience could contribute to systems that keep people safe. Thank you for your consideration.

\vspace{0.5em}

Sincerely, \\
Jonathan Xu

\end{document}
