% !TEX program = xelatex
% Variant: Everbridge -- Staff Software Engineer (Auckland, full-time, permanent).
% Source: https://www.linkedin.com/jobs/view/4423320851/
% Angle: Staff-level full-stack (React + Node.js) on AWS; architecture & scale,
%        end-to-end ownership, code review/mentoring, technology-agnostic + AI-assisted.
%        Honest on Java (has C#/.NET, Go, Node, Python). Auckland local (not contract).

\documentclass{resume}
\usepackage{url}

\begin{document}
\pagenumbering{gobble}

\name{Jonathan Xu}

\basicInfo{
  \email{jonathanilc@hotmail.com} \textperiodcentered\
  \phone{(+64) 21-026-24525} \textperiodcentered\
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}}
  \vspace{2em}

\section*{Summary}
Senior Software Engineer with 10+ years building and operating large-scale, full-stack applications and APIs on AWS -- React and Node.js front to back, with Go, Python, and C\#/.NET across the stack. At IDEXX I lead architecture on an enterprise billing platform serving 5k+ sites and 9k hospitals, owning features end-to-end and driving scalability, clean architecture, and code quality across the team. Technology-agnostic by habit and an everyday user of AI-assisted / agentic coding tools. Auckland-based with full New Zealand working rights. AWS Certified Solutions Architect -- Professional.

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}


\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer -- ezyVet Platform Team} \hfill \textit{2025 -- Present} \\
Leading the architecture of an enterprise billing platform -- refactoring to a vertical-slice design with an OpenAPI-driven REST API -- and raising engineering standards across the team.
\begin{itemize}
  \item Drove architectural decisions to improve scalability and maintainability, migrating to a vertical slice architecture aligned to business domains.
  \item Established OpenAPI as the contract source of truth, enabling generated clients, contract testing, and clearer cross-team APIs.
  \item Lead code reviews and mentor engineers; delivered the migration incrementally with no downtime to the production pipeline.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer -- ezyVet Platform Team} \hfill \textit{2024 -- 2025} \\
Owned, end to end, a large-scale billing platform aggregating and reconciling data from 5k+ sites and 9k hospitals before syncing to SAP for monthly invoicing.
\begin{itemize}
  \item Built Go backend services for high-volume aggregation, validation, and pipeline orchestration; kept them reliable under real enterprise load.
  \item Designed and shipped the React/TypeScript self-service application used by the billing team day to day.
  \item Troubleshot and resolved production data issues; built idempotent delivery and reconciliation against source-of-truth data.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer -- Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar across the full stack -- a React client and Node.js/Express APIs on AWS (ECS/Fargate, S3).
\begin{itemize}
  \item Owned features end-to-end across the React (Context API) client and the Node.js/Express services powering the product.
  \item Managed AWS infrastructure as code with Terraform (ECS/Fargate, S3, VPC, networking); improved deployment reliability and operational visibility.
  \item Containerised services with Docker; troubleshot and maintained stable web-application and API operations.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom full-stack e-commerce solutions for clients on Shopify and BigCommerce.
\begin{itemize}
  \item Built full-stack features and micro-frontend apps embedded in client storefronts, collaborating cross-functionally with clients and designers.
  \item Coached and mentored junior engineers through code review and technical guidance.
  \item Conducted early-phase feasibility research for new features and integrations.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom e-commerce sites; drove DevOps and automation.
\begin{itemize}
  \item Automated the release process and CI/CD pipelines, reducing deploy time and enabling more frequent, reliable releases.
  \item Built reusable components and integrations used across client projects.
  \item Wrote and maintained unit tests to protect critical paths and enable confident refactoring.
\end{itemize}


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Full-Stack: React, Node.js, Express, JavaScript, TypeScript, HTML, CSS, Tailwind, Angular
  \item Languages: JavaScript/TypeScript, Go, Python, C\#/.NET -- technology-agnostic, quick to adopt new languages (e.g. Java)
  \item Cloud \& Infra (AWS): ECS/Fargate, S3, VPC, Terraform, Docker, Kubernetes
  \item Architecture \& Scale: microservices, vertical-slice / clean architecture, OpenAPI-driven contracts, scalability \& performance
  \item AI-Assisted Engineering: everyday use of agentic AI coding tools and AI-in-the-loop development workflows
  \item APIs \& Data: RESTful APIs, GraphQL, SQL/PostgreSQL relational modelling, large-scale data pipelines
  \item Best Practices: code review \& mentoring, SOLID, design patterns, TDD/unit testing, Agile delivery
\end{itemize}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect -- Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: \url{https://github.com/Jonathanilc}
  \item Auckland-based with full New Zealand working rights
  \item Languages: English -- Fluent, Mandarin -- Native speaker
\end{itemize}
\end{document}
