% !TEX program = xelatex
% Variant: Software Consultant (above C1 English) cover letter — small remote IT consulting group.
% Source: https://docs.google.com/document/d/1-pcri7Igy4sDSsTOTjuXoh2nmNefR-_4d2fLXuQKPic/edit
% Angle: client-facing technical liaison + bilingual; honest on native mobile and NZ/US time zones.

\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}

\definecolor{accent}{HTML}{0066CC}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}
\pagenumbering{gobble}

\begin{document}

\begin{flushright}
{\Large\textbf{Jonathan Xu}}\\[0.3em]
\faEnvelope\ \href{mailto:jono_x@icloud.com}{jono\_x@icloud.com} \\
\faPhone\ (+64) 21-026-24525 \\
\faLinkedin\ \href{https://www.linkedin.com/in/jonathan-x-4aba55115}{jonoxu}
\end{flushright}

\vspace{0.5em}

\today

\vspace{0.5em}

Hiring Team \\
Software Consulting Group

\vspace{0.5em}

Dear Hiring Team,

I am writing to apply for your Software Consultant role. The brief — an experienced developer who can run client meetings, represent your senior engineers on calls, and bridge the communication gap for a distributed team whose developers sit in Asia and Europe — is a good fit for what I do well, and I would be glad to support your group's growth.

I have spent 10+ years in software, currently as a senior engineer at IDEXX, and a large part of my work has always been communication rather than just code. I gather requirements directly from stakeholders, run design and scoping conversations, mentor and pair with mid-level engineers, and write the documentation other teams rely on. Earlier, at Moustache Republic, I worked client-facing for several years scoping and delivering custom e-commerce projects. I am comfortable being the person in the room who turns a client's needs into clear direction for the developers building it — and who can speak credibly about the work because I have done it across web, full-stack, and cloud.

Two things may be especially relevant. First, I am a native Mandarin speaker and fluent in English, so I can bridge directly with developers based in Asia as well as with U.S. clients — exactly the gap you describe. Second, I have worked in fully remote, distributed teams across regions for years, so async coordination and the discipline that part-time, overlapping-hours work requires are familiar to me.

I want to be straightforward about two things. My hands-on depth is in web, full-stack, and cloud development; I am conversant across the desktop side (C\#/.NET) but native mobile is not where I have personally written code, so I would lean on your developers' material when representing that work. And I am based in Auckland, New Zealand — I can absolutely commit to a 10–15 hour week overlapping EST or PST business hours, and I would want to confirm a regular schedule that works cleanly for both of us before we begin.

I would welcome a call to discuss how I could help. Thank you for your consideration.

\vspace{0.5em}

Sincerely, \\
Jonathan Xu

\end{document}
