% !TEX program = xelatex
% Variant: Software Consultant (above C1 English) — small remote IT consulting group, contractor 10-15 hrs/week.
% Source: https://docs.google.com/document/d/1-pcri7Igy4sDSsTOTjuXoh2nmNefR-_4d2fLXuQKPic/edit
% Angle: client-facing technical liaison — lead with communication/stakeholder work + bilingual (English fluent / Mandarin native, devs sit in Asia & Europe) + 10+ yrs software breadth. Honest: no hands-on native mobile.

\documentclass{resume}
\usepackage{url}

\begin{document}
\pagenumbering{gobble}

\name{Jonathan Xu}

\basicInfo{
  \email{jono\_x@icloud.com} \textperiodcentered\
  \phone{(+64) 21-026-24525} \textperiodcentered\
  \linkedin[jonoxu]{https://www.linkedin.com/in/jonathan-x-4aba55115}}
  \vspace{2em}

\section*{Summary}
Senior software engineer with 10+ years across web, full-stack, and cloud development, and a strong track record of client- and stakeholder-facing work — running design and requirements conversations, mentoring developers, and translating between business needs and engineering teams. Fluent in English and a native Mandarin speaker, comfortable bridging communication across distributed teams whose developers sit in Asia and Europe. Experienced working remotely and asynchronously across time zones.

\section{\faCogs\ Communication \& Consulting}
\begin{itemize}[parsep=0.5ex]
  \item Client \& stakeholder meetings: gathering requirements, scoping work, and translating client needs into clear direction for development teams.
  \item Mentoring \& technical leadership: pairing with and coaching mid-level engineers, leading code reviews, and representing engineering in cross-team discussions.
  \item Technical writing: authored platform and integration guides used as the reference for other teams.
  \item Distributed delivery: worked in fully remote teams across regions, collaborating asynchronously on design and delivery.
  \item Languages: English — fluent (professional working proficiency); Mandarin — native speaker.
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{IDEXX}, Auckland, New Zealand}{2022 -- Present}
\vspace{1em}
\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2025 -- Present} \\
Lead a platform initiative and act as the point of contact that standardises how internal teams ship and consume services.
\begin{itemize}
  \item Authored the platform's ecosystem guide and API documentation — the reference other engineers rely on day to day.
  \item Standardised service contracts with an OpenAPI-first approach so internal and external consumers integrate without ambiguity.
  \item Coordinate across multiple teams to align on contracts, edge cases, and delivery while keeping production systems running.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – VetSoft Platform Team} \hfill \textit{2024 -- 2025} \\
Delivered an enterprise billing and SAP integration spanning 5,000+ veterinary sites and 9,000 hospitals.
\begin{itemize}
  \item Worked across the wider project team and external vendors to align on requirements, contracts, edge cases, and cutover plans.
  \item Built and shipped a self-service application used directly by the billing team to operate the pipeline — gathering their needs first-hand.
  \item Owned the integration end-to-end, from requirements through delivery and ongoing support conversations.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer – Vet Radar Team} \hfill \textit{2022 -- 2024} \\
Delivered Vet Radar as part of a fully distributed engineering team.
\begin{itemize}
  \item Built and maintained Node.js services and a React client, collaborating asynchronously with teammates across regions and time zones.
  \item Partnered with product and other engineers to turn feature ideas into shippable, well-scoped work.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Moustache Republic}, Auckland, New Zealand}{2018 -- 2022}
\vspace{1em}
\textbf{Senior Software Engineer} \hfill \textit{2020 -- 2022} \\
Delivered custom e-commerce work for clients on Shopify and BigCommerce, working closely with client stakeholders throughout.
\begin{itemize}
  \item Ran client-facing conversations to scope integrations and storefront features, then delivered against them.
  \item Coached and mentored junior team members; wrote and maintained technical documentation.
  \item Conducted feasibility studies and presented options across diverse vendor APIs.
\end{itemize}

\vspace{1em}

\textbf{Software Engineer / DevOps Engineer} \hfill \textit{2018 -- 2020} \\
Delivered custom e-commerce sites and drove delivery automation.
\begin{itemize}
  \item Built reusable components and integrations between storefronts and client back-office systems.
  \item Automated CI/CD pipelines, enabling more frequent and reliable releases.
\end{itemize}

\section{\faLaptop\ Software Breadth}
\begin{itemize}[parsep=0.5ex]
  \item Web \& full-stack: React, Angular, JavaScript, TypeScript, HTML/CSS, Tailwind
  \item Backend: Golang, Node.js, Python (Flask), C\#/.NET Core, RESTful APIs, GraphQL
  \item Cloud \& DevOps (AWS): ECS/Fargate, S3, Kubernetes (EKS), Terraform, Docker, CI/CD (GitHub Actions)
  \item Architecture \& practices: microservices, REST/OpenAPI contracts, Agile/Scrum, TDD/unit testing
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Unitec Institute of Technology}, Auckland, New Zealand}{2016 -- 2018}
\textit{Bachelor of Computing Systems}

\section{\faHeartO\ Licenses \& Certifications}
\begin{itemize}[parsep=0.5ex]
  \item AWS Certified Solutions Architect – Professional
  \item Professional Scrum Master I (PSM I)
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: \url{https://github.com/Jonathanilc}
  \item Availability: remote contractor, comfortable with part-time hours overlapping US (EST/PST) business hours
  \item Working rights: full New Zealand working rights
\end{itemize}
\end{document}
